---
title: "lab4R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab4R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Description
This package will use to find linear regeneration.
package contains different functions whith the help of which we can perform our designer outputs.
following are some functions
which we used for calculating linear regression.

```{r setup}
library(Linreg)
```
Package contain a RC class with name linreg with the help of linreg we will then use functionality and will make a object buy using function in a linreg class which is wiht name l1
below is example of new object of RC class.

Now after making new object from linreg class we will call different functions of RC class class which 
are actually part of linear model.

```{r }

l1 <-  linreg$new(Petal.Length~Species, data = iris)
```
Below is first function which will return resid which is actually in model related to e_hat
with the help of object we will call this function.

```{r }
l1$resid()
```

After residul we have another function of this RC class which is pred which will return predict values which is actually name by hat_y in model.

```{r }
l1$pred()
```
coef() function gives us computed value perform on equation in Rc class.


```{r }
l1$coef()
```

print functions gives us some information which we have use for our linrag class.

```{r }
l1$print()
```
With the help of plot function we will get two plots residuals against fitted and a scale-location plot.

```{r }
l1$plot()
```

Summary function will give us same value as we have in linear model it will return us summary of this RC class containg all the details of model.

```{r }
l1$summary()
```
